---
title: "icomb"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{icomb}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 7
)
```

# Introduction

Forecast reconciliation is used to make forecasts coherent across a hierarchy or grouped structure. In the Australian tourism data, trips can be aggregated by `State`, by `Purpose`, and by their combinations. If forecasts are produced independently for each series, the results will generally not add up correctly across the structure.

This vignette demonstrates a workflow that goes a step further than reconciliation alone. Alongside coherent forecasts, we also examine which series are selected by `icomb`, and whether those series exhibit distinctive time series characteristics.

The analysis proceeds in four stages:

1. construct a grouped tourism structure

2. fit base forecast models and reconcile the forecasts

3. extract series inclusion information from `icomb`

4. relate inclusion of series to feature-based summaries or accuracy of the series.

# Packages

```{r setup, message=FALSE}
library(dplyr)
library(tsibble)
library(fable)
library(icomb)
library(feasts)
library(ggplot2)
library(plotly)
```

# Workflow

## Building a grouped tourism structure

We begin with the `tourism` dataset available in the `tsibble` package and aggregate trips across the `State` and `Purpose` dimensions to create a simple grouped structure.

```{r}
tourism_gts <- tourism |>
  aggregate_key(State * Purpose,
                Trips = sum(Trips))
tourism_gts
```

This grouped structure contains the total, the marginal aggregates (i.e., state level aggregates and purpose level aggregates), and the bottom-level series defined by each `State` and `Purpose` combination. These connected series form a natural setting for forecast reconciliation.

## Fitting base forecasts

We next fit an ETS model to every series in the grouped structure. You can fit any other univariate models or multivariate model(s).

```{r}
fit <- tourism_gts |>
  model(base = ETS(Trips))
fit
```

These are the base forecasts. Since each series is modeled independently, the forecasts are not guaranteed to be coherent with the aggregation constraints.

## Reconciling base forecasts

We reconcile the base forecasts using two methods.

- `ols`: MinT reconciliation with $\mathbf{W}_h \propto \mathbf{I}$

- `icomb`: the `icomb` reconciliation method with group lasso penalty (default option)

```{r}
fit_recon <- fit |>
  reconcile(
    ols = min_trace(base, method = "ols"),
    icomb = icomb(base, train_size = 55)
  )
fit_recon
```

The `icomb` method with group lasso penalty is especially useful for exploratory analysis because it allows us to study which series are included in the information combination process.

## Inspecting reconciliation output

To investigate the behavior of `icomb`, we glance the reconciliation results which provides `.included` variable indicating which series are selected by `icomb` for reconciliation.

```{r}
glance_output <- fit_recon |>
  glance()
glance_output
```

## Computing time series features

To describe the series in the structure statistically, we compute a broad collection of features using **feasts**.

```{r}
tourism_features <- tourism_gts |>
  features(Trips, feature_set(pkgs = "feasts"))
tourism_features
```

These features capture properties such as trend strength, seasonal strength, autocorrelation, linearity, and aspects of forecastability. See the online [Forecasting: Principles and Practice](https://otexts.com/fpp3/features.html) textbook for a detailed description of these features.

Rather than inspecting dozens of features one at a time, it is often useful to summarize them in a smaller feature space.

## Reducing the feature space with PCA

We use principal component analysis (PCA) to obtain a low-dimensional representation of the features.

```{r}
pcs <- tourism_features |>
  select(-State, -Purpose, -zero_run_mean, -zero_start_prop, -zero_end_prop) |>
  prcomp(scale = TRUE) |>
  broom::augment(tourism_features)
pcs
```


The coordinates `.fittedPC1` and `.fittedPC2` summarize the dominant variation across the extracted series features.

## Joining features, node inclusion, and accuracy

To compare statistical features with reconciliation behavior, we join together

- the PCA representation
- the node inclusion indicator from `icomb`, and
- base-model accuracy measures

```{r}
all_info <- glance_output |>
  filter(.model == "icomb") |>
  select(State, Purpose, .included) |>
  full_join(pcs, by = c("State", "Purpose"))

all_info <- accuracy(fit) |>
  select(-.model, -.type) |>
  full_join(all_info, by = c("State", "Purpose"))
all_info
```

This gives a single data frame linking each series to its features, inclusion status, and forecast accuracy metrics.

## Visualizing series inclusion in feature space

A useful first question is whether included and excluded series occupy different regions of the feature space.

```{r}
tourism_viz <- all_info |>
  ggplot(aes(
    x = .fittedPC1,
    y = .fittedPC2,
    colour = .included,
    text = paste0(
      "PC1: ", round(.fittedPC1, 2), "<br>",
      "PC2: ", round(.fittedPC2, 2), "<br>",
      "State: ", State, "<br>",
      "Purpose: ", Purpose, "<br>",
      "MAPE: ", round(MAPE, 2), "<br>",
      "RMSSE: ", round(RMSSE, 2), "<br>",
      "MASE: ", round(MASE, 2)
    )
  )) +
  geom_point()
tourism_viz
```

This plot provides a compact view of whether series inclusion in `icomb` is associated with the broad statistical profile of a series.

For interactive exploration in HTML output, the plot can also be converted with **plotly**.

```{r}
tourism_viz |>
  ggplotly(tooltip = "text")
```


## Examining interpretable features directly

While PCA is useful for summarizing many features at once, it is often easier to interpret individual features directly. Two especially common summaries are trend strength and annual seasonal strength.

```{r}
tourism_feature_plot <- all_info |>
  ggplot(aes(
    x = trend_strength,
    y = seasonal_strength_year,
    colour = .included,
    text = paste0(
      "Trend_strength: ", round(trend_strength, 2), "<br>",
      "Seasonal_strength_year: ", round(seasonal_strength_year, 2), "<br>",
      "State: ", State, "<br>",
      "Purpose: ", Purpose, "<br>"
    )
  )) +
  geom_point()
tourism_feature_plot
```

This plot helps assess whether included series tend to be more strongly trended, more seasonal, or broadly similar to excluded series.

An interactive version can also be produced

```{r}
tourism_feature_plot |>
  ggplotly(tooltip = "text")
```


## Comparing behavior across travel purpose

The relationship between structure and inclusion of series may differ by travel purpose. To explore this, we facet the trend-seasonality display by `Purpose`.

```{r}
tourism_purpose_plot <- all_info |>
  ggplot(aes(
    x = trend_strength,
    y = seasonal_strength_year,
    colour = .included,
    text = paste0(
      "State: ", State, "<br>",
      "Purpose: ", Purpose, "<br>")
  )) +
  geom_point() +
  facet_wrap(vars(Purpose))
tourism_purpose_plot
```

An interactive version can also be produced when desired.

```{r}
tourism_purpose_plot |>
  ggplotly(text = "text")
```

## Interpreting the results

This workflow makes it possible to ask questions such as:

- Do included series tend to be more regular or more forecastable?

- Are highly seasonal series more likely to be selected by `icomb`?

- Is inclusion associated with stronger or weaker base forecast accuracy?

- Do patterns differ systematically across purpose groups?

The answers will depend on the data and the implementation details of `icomb`, but the framework provides a practical way to connect reconciliation output with interpretable series characteristics.

# Beyond summing constraints

The reconciliation methods discussed above are not limited to simple summation constraints. In general, both MinT based approaches and information combination methods can accommodate any *linear* constraints across a system of time series.

At present, the `min_trace()` implementation in **fabletools** is restricted to summing constraints. The `icomb()` approach, however, is more flexible and can be used in settings where the aggregation structure is defined differently.

## Using averages instead of sums

As an illustration, suppose the structure is defined in terms of *averages* rather than totals. We can construct such a grouped structure by aggregating using `mean()` instead of `sum()`.

```{r}
tourism_avg_gts <- tourism_gts |>
  filter(!is_aggregated(State), !is_aggregated(Purpose)) |>
  aggregate_key(State * Purpose,
                Trips = mean(Trips))
```

We then fit and reconcile forecasts in the usual way.

```{r}
fc <- tourism_avg_gts |>
  model(base = ETS(Trips)) |>
  reconcile(icomb = icomb(base, train_size = 55)) |>
  forecast()
```

To verify coherence under this alternative structure, we can recompute the averages from the bottom-level forecasts and compare them with the reconciled values.

```{r}
fc |>
  filter(!is_aggregated(State), !is_aggregated(Purpose), .model == "icomb") |>
  aggregate_key(State * Purpose,
                mean_fc = mean(.mean)) |>
  full_join(fc |> filter(.model == "icomb")) |>
  mutate(diff = mean_fc - .mean) |>
  pull(diff) |>
  range()
```
The range of differences is close to zero.

## Current limitations and extensions

The current implementation of `aggregate_key()` in **fabletools** does not yet support arbitrary weights, which limits direct construction of more general linear constraints. This is expected to be addressed in future releases.

In the meantime, for fully general linear constraints, a practical approach is to manually construct a `tsibble` containing all series in the desired structure and pass it directly to `model()`. This provides complete flexibility in defining relationships among the series.





